iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-29 manuscript/main.tex
ECM credit
Cleaned up use case descriptions.

iSEE automatically memorizes the exact R code that was used to generate every plot, extending previous work by \cite{marini2016interrepro}.
This code is fully accessible to users at any time during the run-time of the interface.
By integrating the code reported by iSEE into their own scripts, users to easily reproduce the results of any exploratory analysis.
Similarly, the code required to reproduce the current state of the interface can also be generated.
This can be used in startup scripts to launch an iSEE instance in any preferred layout, including the panel organization, variable selection, colouring schemes, links between panels and even individual brushes and lasso selections.

@@

\section*{Use cases} % FM: used often in other software articles in F1000res
To demonstrate the functionalities and flexibility of the iSEE package, we applied our method to a number of publicly available datasets.
Details are provided in the tour subfolder of the GitHub repository for this manuscript (\url{https://github.com/LTLA/iSEE2018}), and for each dataset a combination of \_app.R and \_tour.txt is provided.
An instance of iSEE running on the respective datasets is provided as a stand-alone webpages, for demonstration purposes without the need for any software installation.

\subsection*{Single-cell plate-based RNA-seq}
% TODO: better title, or do we drop this allen section altogether?
We demonstrate the application of iSEE to examine a subset of 379 cells from of mouse visual cortex \citep{tasic2016allen}.
This example can be reproduced locally after installation of the iSEE package with the following code:

\begin{lstlisting}[language=R]
library(iSEE)
example(iSEE, ask = F)
\end{lstlisting}

@@

\subsection*{Single-cell droplet-based RNA-seq}
% TODO: better title, or do we drop the allen section altogether (above)?
We also demonstrate the use of iSEE to explore a larger data set of 4,000 PBMC single-cell RNA-sequencing dataset from 10X Genomics \citep{zheng2017massively}.
% TODO: take out the juice from what the tour does, and maybe one figure/screenshot in each case?

% TODO: embed the allen demo data set
Link: \url{http://shiny.imbei.uni-mainz.de:3838/iSEE_PBMC4k/}

\subsection*{Bulk RNA-seq from TCGA}
We also demonstrate how iSEE seamlessly scales up with larger data sets as the TCGA RNA-seq collection of measurements for 23,368 genes across 7,706 tumor samples \citep{piccolo2015TCGA}.
% TODO: take out the juice from what the tour does, and maybe one figure/screenshot in each case?

% TODO: embed the TCGA demo data set
Link: \url{http://shiny.imbei.uni-mainz.de:3838/iSEE_TCGA/}

\subsection*{CyTOF}
Lastly, we also showcase the use of iSEE to vizualise and refine a gating analysis, followed by the investigation of a functional marker between two sample groups, using a published mass cytometry (CyTOF) data set \citep{bodenmiller2012cytof}.
% TODO: take out the juice from what the tour does, and maybe one figure/screenshot in each case?

>>>>

iSEE automatically memorizes the exact R code that was used to generate every plot, extending previous work by \cite{marini2016interrepro}.
This code is fully accessible to users at any time during the run-time of the interface.
By integrating the code reported by iSEE into their own scripts, users can easily reproduce the results of any exploratory analysis.
Similarly, the code required to reproduce the current state of the interface can also be reported.
This can be used in startup scripts to launch an iSEE instance in any preferred layout, including the panel organization, variable selection, colouring schemes, links between panels and even individual brushes and lasso selections.

@@

\section*{Use cases} % FM: used often in other software articles in F1000res

\subsection*{Plate-based single-cell RNA sequencing}
To demonstrate iSEE's functionality, we used it to explore a plate-based single-cell RNA sequencing (scRNA-seq) data set.
We used a subset of data from a study involving cells from the mouse visual cortex \citep{tasic2016allen}.
This demonstration guides the user through the main features of the iSEE interface, including the multi-panel layout, colouring options and dynamic linking.\\

@@

\subsection*{Droplet-based single-cell RNA sequencing}
We applied iSEE to a larger scRNA-seq data set involving 4,000 peripheral blood mononuclear cells (PBMCs), generated by 10X Genomics \citep{zheng2017massively}.
This demonstration explores the differences between different methods for distinguishing cells from empty droplets in droplet-based scRNA-seq protocols \citep{lun2018distinguishing}.\\

Link: \url{http://shiny.imbei.uni-mainz.de:3838/iSEE_PBMC4k/}

\subsection*{Bulk RNA sequencing from TCGA}
We applied iSEE to bulk RNA sequencing data from The Cancer Genome Atlas (TCGA) project, using a subset of expression profiles involving 7,706 tumor samples \citep{piccolo2015TCGA}.
This demonstration examines the elevation of \textit{HER2} expression in breast cancer samples.\\

Link: \url{http://shiny.imbei.uni-mainz.de:3838/iSEE_TCGA/}

\subsection*{Mass cytometry}
Finally, we explored a mass cytometry study involving PBMCs from multiple donors before and after stimulation with BCR/FcR-XL \citep{bodenmiller2012cytof}.
We used iSEE to vizualise and refine a gating analysis to obtain B cells, and to investigate differences in expression of the functional marker pS6 after stimulation.\\
